Worflow

### 2017-06-09 R/workflow.Rmd
changes to plotHeatmap code

```{r heatmap }
plotHeatmap(ceObj, clusterSamplesData = "dendrogramValue", 
            breaks = .99)
```

@@

```{r}
# sampleData <- data.frame(ours = primaryCluster(ceObj))
# plotHeatmap(assays(se)$normalizedValues,
#             main = 'Normalized values, 1000 most variable genes',
#             clusterSamplesData = ceObj@dendro_samples,
#             sampleData = as.matrix(sampleData),clusterLegend=ceObj@clusterLegend[1])
# easier fix:
plotHeatmap(ceObj, visualizeData = assays(se)$normalizedValues,
            whichClusters = "primary",
            clusterSamplesData = "dendrogramValue",
            main = 'Normalized values, 1000 most variable genes',
            breaks = 0.99)

>>>>

EP: Agreed

```{r heatmap, eval=FALSE}
plotHeatmap(ceObj, clusterSamplesData = "dendrogramValue", 
            breaks = .99)
```

@@

EP: We should be careful, because the default in plotHeatmap is to plot the 500 most variable genes (maybe a slightly paternalistic default). I've changed it to `all` in the code here. I've also added the plotting of the batch, experiment, and Russell's original clusters. We may not want to keep all of them, but probably at least Russell's clusters for comparison.

```{r}
# sampleData <- data.frame(ours = primaryCluster(ceObj))
# plotHeatmap(assays(se)$normalizedValues,
#             main = 'Normalized values, 1000 most variable genes',
#             clusterSamplesData = ceObj@dendro_samples,
#             sampleData = as.matrix(sampleData),clusterLegend=ceObj@clusterLegend[1])
# easier fix:
origClusterColors<-bigPalette[1:nlevels(colData(ceObj)$clusterLabels)]
experimentColors<-bigPalette[1:nlevels(colData(ceObj)$Experiment)]
batchColors<-bigPalette[1:nlevels(colData(ceObj)$Batch)]
metaColors<-list("Experiment"=experimentColors,"Batch"=batchColors,"clusterLabels"=origClusterColors)

plotHeatmap(ceObj, visualizeData = assays(se)$normalizedValues,
            whichClusters = "primary",clusterFeaturesData="all",
            clusterSamplesData = "dendrogramValue",
			sampleData=c("clusterLabels","Batch","Experiment"), clusterLegend=metaColors, annLegend=FALSE,
            main = 'Normalized values, 1000 most variable genes',
            breaks = 0.99)
